### 2021-02-25 code/BW_graph_20200203.Rmd
reinitiate the project; copy haipeng's rmd file in

---
title: "CS2019_BW"
author: "HPSUN"
date: "3/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## library
```{r }
library(tidyverse)
library(readxl)
library(agricolae)
library(Hmisc)
library(conflicted)
library(nlme)
library(effects)
conflict_scout()
conflict_prefer("filter", "dplyr")
conflict_prefer("summarize", "dplyr")
```

## function
```{r}
flat_matrix = function(mat){ 
    ### flat the matrix into dataframe with name and value.
    res = matrix(NA, nrow = nrow(mat)*ncol(mat), ncol = 2)
    res = as.data.frame(res)
    colnames(res) = c("cell_name","cell_value")
    for(nr in 1:nrow(mat)){
        row_name = rownames(mat)[nr]
        for(nc in 1:ncol(mat)){
            col_name = colnames(mat)[nc]
            nres = (nr-1)*ncol(mat) + nc
            res[nres,"cell_name"] = paste(sort(c(row_name,col_name)),collapse = "_")
            res[nres,"cell_value"] = mat[nr,nc]
        }
    }
    res
}

```

## data
```{r message=FALSE, warning=FALSE}
dat = read_excel("MasterMetadata-CS-SW-Oct2019-20210202-HS.xlsx",sheet = "BodyWeightRecords")
dat = dat %>% filter(Sex != "?")
# 3 animial was losing weight during week 4, cageID 190, need to exclude them for the analysis
dat = dat %>% filter(!(TimePoint_Weeks == 4 & CageID == "C190"))

dat_summary = dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% 
    dplyr::summarize(BW_mean = mean(Weight_g),
              N_sample = n(),
              BW_sd = sd(Weight_g),
              BW_se = BW_sd/sqrt(N_sample-1),
              BW_max = max(Weight_g),
              BW_min = min(Weight_g)
              )

dat_summary = dat_summary %>% 
    group_by(TimePoint_Weeks) %>% 
    mutate(BW_min_temp = min(BW_mean)) %>%
    ungroup() %>%
    mutate(N_y_temp = case_when(
            BirthMode == "VF" & Sex == "F" ~ 9,
            BirthMode == "VF" & Sex == "M" ~ 5,
            BirthMode == "CSR" & Sex == "F" ~ 8,
            BirthMode == "CSR" & Sex == "M" ~ 4,
            BirthMode == "CS" & Sex == "F"~ 7,
            BirthMode == "CS" & Sex == "M"~ 3),
           N_y = BW_min_temp - N_y_temp) %>% 
    select(-N_y_temp, - BW_min_temp)

dat_stat = matrix(NA, nrow = length(unique(dat$TimePoint_Weeks))*6, ncol = 6)
colnames(dat_stat) = c("TimePoint_Weeks", "Sex", "Comparsion", "P_val_wilcox", "Rank_diff", "P_val_kruskal")
dat_stat = as.data.frame(dat_stat)
for (i in sort(unique(dat$TimePoint_Weeks))){
    for (g in c("F","M")){
        dat_temp = dat %>% filter(TimePoint_Weeks == i, Sex == g)        
        temp = pairwise.wilcox.test(dat_temp$Weight_g, 
                                    dat_temp$BirthMode, 
                                    p.adjust.method = "none", 
                                    paired = F)
        p_temp = flat_matrix(temp$p.value) %>% 
            na.omit() %>% 
            arrange(cell_name)
        if(g == "F") {
            nrange = (i-1)*6 + 1:3
        }else{
            nrange = (i-1)*6 + 4:6
        }
        p_kruskal = with(dat_temp, kruskal(Weight_g, BirthMode, p.adj = "none", main="dat_temp", group=F))
        dat_stat[nrange,"TimePoint_Weeks"] = i
        dat_stat[nrange,"Sex"] = g
        dat_stat[nrange,"Comparsion"] = p_temp$cell_name
        dat_stat[nrange,"P_val_wilcox"] = p_temp$cell_value
        dat_stat[nrange,"Rank_diff"] = p_kruskal$comparison$Difference
        dat_stat[nrange,"P_val_kruskal"] = p_kruskal$comparison$pvalue
    } 
}

dat_stat %>% filter(P_val_wilcox < 0.1 | P_val_kruskal < 0.1) %>% arrange(Sex, TimePoint_Weeks)

```

## aov + MRT
```{r}
dat_stat_2 = matrix(NA, nrow = 1, ncol = 18)
colnames(dat_stat_2) = c("TimePoint_Weeks", "Sex", "BirthMode", "BW_mean", "N_sample", "BW_max", "BW_min", "boot.lo", "boot.up", "P_norm",  "lm.pval", "lm.effect","groups", "lm.lo", "lm.up", "lme.effect", "lme.lo", "lme.up")
dat_stat_2 = as.data.frame(dat_stat_2)

i = 10
g = "F"

for (i in sort(unique(dat$TimePoint_Weeks))){
    for (g in c("F","M")){
        dat_temp = dat %>% filter(TimePoint_Weeks == i, Sex == g)
        wk = dat_temp %>% split(., .$BirthMode)
        out.ci = sapply(wk, function(x){smean.cl.boot(x$Weight_g, conf.int = .95, B = 1000, na.rm = T, reps = F)}) %>% 
            t() %>% as.data.frame() %>% rownames_to_column(var = "BirthMode") %>% 
            rename(boot.lo = Lower, boot.up = Upper) %>% select(BirthMode, boot.lo, boot.up)

        out.norm = sapply(wk, function(x){shapiro.test(x$Weight_g)}) %>% t() %>% as.data.frame() %>% 
            rownames_to_column(var = "BirthMode") %>% 
            mutate(P_norm = unlist(p.value)) %>% select(BirthMode,P_norm)

        m_1 = aov(Weight_g ~ BirthMode, data = dat_temp)
        p_m1 = summary(m_1)[[1]]["BirthMode",'Pr(>F)']
        out_m1 = duncan.test(m_1,"BirthMode")
        res = merge(out_m1$means, out_m1$groups, by.x = 0, by.y = 0) %>% 
            rename(BirthMode = Row.names, BW_mean = Weight_g.x, N_sample = r, BW_max = Max, BW_min = Min) %>% 
            select(BirthMode, BW_mean, N_sample, BW_max, BW_min, groups)
        res = res %>% left_join(out.ci, by = "BirthMode") %>% left_join(out.norm, by = "BirthMode") %>% mutate(lm.pval = p_m1)
        e_m1 = allEffects(m_1)
        res_temp = cbind(e_m1$BirthMode$x, e_m1$BirthMode$fit, e_m1$BirthMode$lower, e_m1$BirthMode$upper) 
        names(res_temp) = c("BirthMode", "lm.effect","lm.lo","lm.up")
        res = res %>% left_join(res_temp, by = "BirthMode")

        m_2 = lme(Weight_g ~ BirthMode, random = ~1 | FamilyID, data = dat_temp, method = "REML")
        e_m2 = allEffects(m_2)
        res_temp = cbind(e_m2$BirthMode$x, e_m2$BirthMode$fit, e_m2$BirthMode$lower, e_m2$BirthMode$upper) 
        names(res_temp) = c("BirthMode", "lme.effect",  "lme.lo","lme.up")
        res = res %>% left_join(res_temp, by = "BirthMode") %>% mutate(TimePoint_Weeks = i, Sex = g) %>% 
            select(TimePoint_Weeks, Sex, BirthMode, BW_mean, N_sample, BW_max, BW_min, boot.lo, boot.up, P_norm,  lm.pval, lm.effect, groups, lm.lo, lm.up, lme.effect, lme.lo, lme.up)
        dat_stat_2 = rbind(dat_stat_2,res)
    }
}

dat_stat_2 = na.omit(dat_stat_2)

dat_stat_2 = dat_stat_2 %>% 
    group_by(TimePoint_Weeks) %>% 
    mutate(BW_min_temp = min(BW_mean)) %>%
    ungroup() %>%
    mutate(N_y_temp = case_when(
            BirthMode == "VF" & Sex == "F" ~ 9,
            BirthMode == "VF" & Sex == "M" ~ 5,
            BirthMode == "CSR" & Sex == "F" ~ 8,
            BirthMode == "CSR" & Sex == "M" ~ 4,
            BirthMode == "CS" & Sex == "F"~ 7,
            BirthMode == "CS" & Sex == "M"~ 3),
           N_y = BW_min_temp - N_y_temp) %>% 
    select(-N_y_temp, - BW_min_temp)

knitr::kable(dat_stat_2 %>% filter(lm.pval < 0.05) %>% arrange(Sex, TimePoint_Weeks))

```

## plot
```{r fig.height=6, fig.width=12}
Sex.labs = c("Male","Female")
names(Sex.labs) <- c("M","F")

p1 = ggplot(data = dat_stat_2, aes(x = TimePoint_Weeks, y = BW_mean, 
                               ymin = boot.lo, ymax = boot.up,
                               color = BirthMode)) +
    geom_line(aes(group = BirthMode),size = 1.5) + 
    geom_ribbon(aes(group = BirthMode,fill = BirthMode), alpha = 0.2) + 
    geom_text(aes(x = TimePoint_Weeks,y = N_y, label = N_sample), 
              position = position_dodge2(width = 0.5,padding = 0.3), size = 3) +
#    geom_line(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode, group = MouseID),
#              alpha = 0.2, inherit.aes=FALSE) + 
#    geom_point(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode, shape = BirthMode), 
#               alpha = 0.5, size =1,inherit.aes=FALSE) +  
    scale_x_continuous(breaks = seq(1, max(dat_stat_2$TimePoint_Weeks) + 1, by = 1)) + 
    scale_y_continuous(breaks = seq(0, max(dat_stat_2$BW_max) + 1, by = 5 )) +
    labs(x = "Week", y = "Body Weight (g)") + 
    facet_wrap(~Sex, labeller = labeller(Sex = Sex.labs)) + 
    theme_bw() + theme(panel.background = element_rect(fill = NA), 
                       plot.title = element_text(hjust = 0.5), 
                       text = element_text(face = 'bold'),
                       strip.text = element_text(face = "bold",size=12),
                       axis.text = element_text(face = "bold",size = 10))
print(p1)

p2 = ggplot(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
    geom_smooth() + 
    geom_text(data = dat_stat_2, aes(x = TimePoint_Weeks,y = N_y, label = N_sample), 
              position = position_dodge2(width = 0.5,padding = 0.3), size = 3) +
    scale_x_continuous(breaks = seq(1, max(dat_stat_2$TimePoint_Weeks) + 1, by = 1)) + 
    scale_y_continuous(breaks = seq(0, max(dat_stat_2$BW_max) + 1, by = 5 )) +
    labs(x = "Week", y = "Body Weight (g)") + 
    facet_wrap(~Sex, labeller = labeller(Sex = Sex.labs)) + 
    theme_bw() + theme(panel.background = element_rect(fill = NA), 
                       plot.title = element_text(hjust = 0.5), 
                       text = element_text(face = 'bold'),
                       strip.text = element_text(face = "bold",size=12),
                       axis.text = element_text(face = "bold",size = 10))

print(p2)

```

## body weight gain
```{r}
dat = read_excel("MasterMetadata-CS-SW-Oct2019-20210202-HS.xlsx",sheet = "BodyWeightRecords")
dat = dat %>% filter(Sex != "?")
# 3 animial was losing weight during week 4, cageID 190, need to exclude them for the analysis
dat = dat %>% filter(!(TimePoint_Weeks == 4 & CageID == "C190"))

BWgain= dat %>% filter(TimePoint_Weeks > 2) %>% arrange(MouseID, TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(BW_gain = Weight_g - Weight_g[1], N = n()) %>% filter(TimePoint_Weeks > 3)

```

```{r}
BWgain_stat_2 = matrix(NA, nrow = 1, ncol = 18)
colnames(BWgain_stat_2) = c("TimePoint_Weeks", "Sex", "BirthMode", "BWgain_mean", "N_sample", "BWgain_max", "BWgain_min", "boot.lo", "boot.up", "P_norm",  "lm.pval", "lm.effect","groups", "lm.lo", "lm.up", "lme.effect", "lme.lo", "lme.up")
BWgain_stat_2 = as.data.frame(BWgain_stat_2)

i = 10
g = "F"

for (i in sort(unique(BWgain$TimePoint_Weeks))){
    for (g in c("F","M")){
        dat_temp = BWgain %>% filter(TimePoint_Weeks == i, Sex == g)
        wk = dat_temp %>% split(., .$BirthMode)
        out.ci = sapply(wk, function(x){smean.cl.boot(x$BW_gain, conf.int = .95, B = 1000, na.rm = T, reps = F)}) %>% 
            t() %>% as.data.frame() %>% rownames_to_column(var = "BirthMode") %>% 
            rename(boot.lo = Lower, boot.up = Upper) %>% select(BirthMode, boot.lo, boot.up)

        out.norm = sapply(wk, function(x){shapiro.test(x$BW_gain)}) %>% t() %>% as.data.frame() %>% 
            rownames_to_column(var = "BirthMode") %>% 
            mutate(P_norm = unlist(p.value)) %>% select(BirthMode,P_norm)

        m_1 = aov(BW_gain ~ BirthMode, data = dat_temp)
        p_m1 = summary(m_1)[[1]]["BirthMode",'Pr(>F)']
        out_m1 = duncan.test(m_1,"BirthMode")
        res = merge(out_m1$means, out_m1$groups, by.x = 0, by.y = 0) %>% 
            rename(BirthMode = Row.names, BWgain_mean = BW_gain.x, N_sample = r, BWgain_max = Max, BWgain_min = Min) %>% 
            select(BirthMode, BWgain_mean, N_sample, BWgain_max, BWgain_min, groups)
        res = res %>% left_join(out.ci, by = "BirthMode") %>% left_join(out.norm, by = "BirthMode") %>% mutate(lm.pval = p_m1)
        e_m1 = allEffects(m_1)
        res_temp = cbind(e_m1$BirthMode$x, e_m1$BirthMode$fit, e_m1$BirthMode$lower, e_m1$BirthMode$upper) 
        names(res_temp) = c("BirthMode", "lm.effect","lm.lo","lm.up")
        res = res %>% left_join(res_temp, by = "BirthMode")

        m_2 = lme(BW_gain ~ BirthMode, random = ~1 | FamilyID, data = dat_temp, method = "REML")
        e_m2 = allEffects(m_2)
        res_temp = cbind(e_m2$BirthMode$x, e_m2$BirthMode$fit, e_m2$BirthMode$lower, e_m2$BirthMode$upper) 
        names(res_temp) = c("BirthMode", "lme.effect",  "lme.lo","lme.up")
        res = res %>% left_join(res_temp, by = "BirthMode") %>% mutate(TimePoint_Weeks = i, Sex = g) %>% 
            select(TimePoint_Weeks, Sex, BirthMode, BWgain_mean, N_sample, BWgain_max, BWgain_min, boot.lo, boot.up, P_norm,  lm.pval, lm.effect, groups, lm.lo, lm.up, lme.effect, lme.lo, lme.up)
        BWgain_stat_2 = rbind(BWgain_stat_2,res)
    }
}

BWgain_stat_2 = na.omit(BWgain_stat_2)

BWgain_stat_2 = BWgain_stat_2 %>% 
    group_by(TimePoint_Weeks) %>% 
    mutate(BWgain_min_temp = min(BWgain_mean)) %>%
    ungroup() %>%
    mutate(N_y_temp = case_when(
            BirthMode == "VF" & Sex == "F" ~ 6,
            BirthMode == "VF" & Sex == "M" ~ 3,
            BirthMode == "CSR" & Sex == "F" ~ 5,
            BirthMode == "CSR" & Sex == "M" ~ 2,
            BirthMode == "CS" & Sex == "F"~ 4,
            BirthMode == "CS" & Sex == "M"~ 1),
           N_y = BWgain_min_temp - N_y_temp) %>% 
    select(-N_y_temp, - BWgain_min_temp)

knitr::kable(BWgain_stat_2 %>% filter(lm.pval < 0.05) %>% arrange(Sex, TimePoint_Weeks))
```

## plot
```{r fig.height=6, fig.width=12}
Sex.labs = c("Male","Female")
names(Sex.labs) <- c("M","F")

p1 = ggplot(data = BWgain_stat_2, aes(x = TimePoint_Weeks, y = BWgain_mean, 
                               ymin = boot.lo, ymax = boot.up,
                               color = BirthMode)) +
    geom_line(aes(group = BirthMode),size = 1.5) + 
    geom_ribbon(aes(group = BirthMode,fill = BirthMode), alpha = 0.2) + 
    geom_text(aes(x = TimePoint_Weeks,y = N_y, label = N_sample), 
              position = position_dodge2(width = 0.5,padding = 0.3), size = 3) +
#    geom_line(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode, group = MouseID), alpha = 0.2, inherit.aes=FALSE) + 
#    geom_point(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode, shape = BirthMode), alpha = 0.5, size =1,inherit.aes=FALSE) +  
    scale_x_continuous(breaks = seq(1, max(BWgain_stat_2$TimePoint_Weeks) + 1, by = 1)) + 
    scale_y_continuous(breaks = seq(0, max(BWgain_stat_2$BWgain_max) + 1, by = 5 )) +
    labs(x = "Week", y = "Body Weight Gain (g)") + 
    facet_wrap(~Sex, labeller = labeller(Sex = Sex.labs)) + 
    theme_bw() + theme(panel.background = element_rect(fill = NA), 
                       plot.title = element_text(hjust = 0.5), 
                       text = element_text(face = 'bold'),
                       strip.text = element_text(face = "bold",size=12),
                       axis.text = element_text(face = "bold",size = 10))
print(p1)
#y_zoom = max(dat_summary[which(dat_summary$TimePoint_Weeks==6),"BW_max"]) + 5
#p1 + coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-2, y_zoom))

p2 = ggplot(data = BWgain, aes(x = TimePoint_Weeks, y = BW_gain, color = BirthMode)) +
#    geom_line(aes(group = MouseID)) + 
    geom_smooth(method = "loess") + 
    geom_text(data = BWgain_stat_2, aes(x = TimePoint_Weeks,y = N_y, label = N_sample), 
              position = position_dodge2(width = 0.5,padding = 0.3), size = 3) +
#    geom_line(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode, group = MouseID), alpha = 0.2, inherit.aes=FALSE) + 
#    geom_point(data = dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode, shape = BirthMode), alpha = 0.5, size =1,inherit.aes=FALSE) +  
    scale_x_continuous(breaks = seq(1, max(BWgain$TimePoint_Weeks) + 1, by = 1)) + 
    scale_y_continuous(breaks = seq(0, max(BWgain$BW_gain) + 1, by = 5 )) +
    labs(x = "Week", y = "Body Weight Gain (g)") + 
    facet_wrap(~Sex, labeller = labeller(Sex = Sex.labs)) + 
    theme_bw() + theme(panel.background = element_rect(fill = NA), 
                       plot.title = element_text(hjust = 0.5), 
                       text = element_text(face = 'bold'),
                       strip.text = element_text(face = "bold",size=12),
                       axis.text = element_text(face = "bold",size = 10))
print(p2)

```

### 2021-02-25 code/draft.Rmd
reinitiate the project; copy haipeng's rmd file in

---
title: "draft"
author: "Jincheng Wang"
date: "7/2/2020"
output: html_document
---

## Preparation
1. Setup
```{r setup, message=FALSE, warning=FALSE}
# Loading library here
library(conflicted)
library(knitr)
library(tidyverse)
library(extrafont)
library(readxl)
library(ggrepel)
library(ggpubr)

conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")

options(max.print="75")
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, warning = FALSE, prompt=FALSE, tidy = TRUE, comment = NA, message = FALSE)
opts_knit$set(width=75)

# set path
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(rprojroot::find_rstudio_root_file())
## path to data record on dropbox
path_rec <- "~/Dropbox/MGDB-Shared/CSR 2019 SW/ExperimentRecords/"
list.files(path_rec)

# number of cores/thread to use
nc <- switch(Sys.info()[['sysname']], Windows = 1, Darwin = 4, Linux = 12)

source("~/Dropbox/42-JCHWANG-RUTGERS/Projects-Rutgers/Src/utils.R")

sessionInfo()
```

## Body weight
### Overall, plotting all data
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

# BW <- BW %>% filter(!FamilyID %in% c("VF1", "CSR1") )
current_days <- max(BW$TimePoint_Days)

BW_sum <- BW %>% group_by(TimePoint_Days, BirthMode, Sex) %>% summarise(N = n(), Mean = mean(Weight_g), SE = sd(Weight_g)/sqrt(N-1))

y_max <- ceiling(max(BW$Weight_g)/4)*4
ggplot(BW, aes(x = TimePoint_Days, y = Weight_g, color = BirthMode)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_path(aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
    geom_text_repel(data = BW_sum, aes(x = TimePoint_Days, y = Mean, label = N), size = 4, show.legend = F) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(7, current_days, 7)), labels = c(seq(7, current_days, 7))/7) + 
    scale_y_continuous(breaks = seq(2, y_max, 4)) +
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight Plots-AllData") +
    theme_Publication() + theme(panel.grid.minor = element_blank())
```

### Summary table
```{r}
BW_sum2 <- BW %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n(), N_batch = unique(Batch) %>% length, N_family = unique(FamilyNo) %>% length(), Mean = mean(Weight_g), SE = sd(Weight_g)/sqrt(N))

BW_sum2 %>% mutate(Count = paste0(N, "(", N_family, ")")) %>% select(BirthMode, Sex, TimePoint_Weeks, Count) %>% spread(key = TimePoint_Weeks, value = Count) %>% View
```

### Detailed plot
```{r}
date_range <- c(2, BW_sum2$TimePoint_Weeks[BW_sum2$N_family>=5] %>% max)

BW_dat <- BW %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])

BW_dat_stat_sum <- BW_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_g) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup

BW_dat_test_sum <- split(BW_dat, f = list(BW_dat$TimePoint_Weeks, BW_dat$Sex)) %>% lapply(., function(x){(aov(Weight_g ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})

BW_dat_test_sum2 <- lapply(seq_along(BW_dat_test_sum), function(x){BW_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))

ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
    geom_point(data = BW, size = 0.5, alpha = 0.5) +
    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10. After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
set_panel_size(file = "results/figs/exploratory/BW.pdf", width = unit(4, "in"), height = unit(3.2, "in"), useDingbats = F)
```

## Body Weight gain relative to week 2
```{r}
BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))

BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks!=1) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])

date_range <- c(2, 10)

BW_f_dat <- BW_f %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])

BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n())

%>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup

BW_dat_test_sum <- split(BW_dat, f = list(BW_dat$TimePoint_Weeks, BW_dat$Sex)) %>% lapply(., function(x){(aov(Weight_g ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})

BW_dat_test_sum2 <- lapply(seq_along(BW_dat_test_sum), function(x){BW_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))

ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
    geom_point(data = BW, size = 0.5, alpha = 0.5) +
    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
    facet_grid(.~Sex) +
    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10. After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))

```

## DEXA
```{r}
MM <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "MouseMetadata")

MM_dexa <- MM %>% filter(ExperimentSet=="Set1-BW", ReasonTermination %in% c("DEXA", "Week18Termination")) %>% mutate(TimePoint_Weeks = ifelse(ReasonTermination=="DEXA", 6, 18))

MM_dexa %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N_family = length(unique(FamilyID)), N = length(unique(MouseID))) %>% mutate(Count = paste0(N, " (", N_family, ")")) %>% select(BirthMode, Sex, TimePoint_Weeks, Count) %>% spread(key = TimePoint_Weeks, value = Count) %>% View

spread(key = Sex, value = N)
```

## Behavior
```{r}
Beh <- read_excel(paste0(path_rec, "BehaviorAnimalMetadata-20190124-JW.xlsx"))

Beh %>% filter(Batch != "NA") %>% group_by(BirthMode, Sex) %>% summarise(N_family = length(unique(FamilyID)), N = length(unique(MouseNo))) %>%  mutate(Count = paste0(N, " (", N_family, ")")) 
```

## Feces

```{r}
MM <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "SampleMetadata")
MM_fec <- MM %>% filter(BodySite=="Feces")
MM_fec$TimePointInWeeks[MM_fec$TimePointInWeeks %in% c(11, 14)] = "11/14"

MM_fec %>% group_by(TimePointInWeeks, BirthMode, Sex) %>% summarise(N_family = length(unique(FamilyID)), N = length(unique(MouseID))) %>% mutate(Count = paste0(N, " (", N_family, ")")) %>% select(BirthMode, Sex, TimePointInWeeks, Count) %>% spread(key = TimePointInWeeks, value = Count) %>% View
```

## Sac
```{r}
MM <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "SampleMetadata")
Sac <- MM %>% filter(!SampleType %in% c("Feces", "Empty"))
Sac$BirthMode[Sac$BirthMode=="VD"] <- "VF"

Sac %>% group_by(TimePointInWeeks, BirthMode, Sex) %>% summarise(N_family = length(unique(FamilyID)), N = length(unique(MouseID))) %>% mutate(Count = paste0(N, " (", N_family, ")")) %>% select(BirthMode, Sex, TimePointInWeeks, Count) %>% spread(key = TimePointInWeeks, value = Count) %>% View

```

### 2021-02-25 code/BW_graph_20200203.Rmd
updated draft.Rmd with a little more

@@
 library(effects)
-conflict_scout()
-conflict_prefer("filter", "dplyr")
-conflict_prefer("summarize", "dplyr")
+# conflict_scout()
+# conflict_prefer("filter", "dplyr")
+# conflict_prefer("summarize", "dplyr")
 ```

### 2021-02-25 code/draft.Rmd
updated draft.Rmd with a little more

@@
 # Loading library here
-library(conflicted)
 library(knitr)
 library(tidyverse)
-library(extrafont)
 library(readxl)
 library(ggrepel)
-library(ggpubr)
-
-conflict_prefer("filter", "dplyr")
-conflict_prefer("lag", "dplyr")
+# library(ggpubr)
 
@@
 ## path to data record on dropbox
-path_rec <- "~/Dropbox/MGDB-Shared/CSR 2019 SW/ExperimentRecords/"
+path_rec <- "~/Dropbox/IFNH CSR/ExperimentRecords/"
 list.files(path_rec)
@@
 ```{r}
-BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
+BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20210224-HS.xlsx"), sheet = "BodyWeightRecords", range = "A1:T2009") %>% filter(!is.na(Weight_g))
 BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))
@@
 
-BW_sum <- BW %>% group_by(TimePoint_Days, BirthMode, Sex) %>% summarise(N = n(), Mean = mean(Weight_g), SE = sd(Weight_g)/sqrt(N-1))
+BW_sum <- BW %>% group_by(TimePoint_Days, BirthMode, Sex) %>% summarise(N = n(), Mean = mean(Weight_g), SE = sd(Weight_g)/sqrt(N))
 
@@
     labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight Plots-AllData") +
-    theme_Publication() + theme(panel.grid.minor = element_blank())
+    theme_jw() + theme(panel.grid.minor = element_blank())
 ```
@@
 
-BW_dat <- BW %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])
+BW_dat <- BW %>% dplyr::filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])
 
@@
     scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10.
-After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
-    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted; ANOVA test with duncan's multiple range tests were performed at each week ", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
 set_panel_size(file = "results/figs/exploratory/BW.pdf", width = unit(4, "in"), height = unit(3.2, "in"), useDingbats = F)
@@
 
-## Body Weight gain relative to week 2
+## Body Weight gain relative to week 3
 ```{r}
-BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
-BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))
+BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])
 
-BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks!=1) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])
-
-date_range <- c(2, 10)
+date_range <- c(4, 16)
 
@@
 
-BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n())
+BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(names_from = c(BirthMode, Sex), values_from = N)
 
-%>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
+BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
 
-BW_dat_test_sum <- split(BW_dat, f = list(BW_dat$TimePoint_Weeks, BW_dat$Sex)) %>% lapply(., function(x){(aov(Weight_g ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})
+BW_f_dat_test <- BW_f_dat %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain ~ BirthMode, p.adjust.method = "none") %>% ungroup() %>% mutate(p.adj = p.adjust(p, method = "fdr"))
 
-BW_dat_test_sum2 <- lapply(seq_along(BW_dat_test_sum), function(x){BW_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
+BW_f_dat_test_tbl1 <- BW_f_dat_test %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p.adj)
 
-ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
-    geom_point(data = BW, size = 0.5, alpha = 0.5) +
-    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
-    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
-    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
-    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
-    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
-    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
-    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
+BW_f_dat_test_sum <- split(BW_f_dat, f = list(BW_f_dat$TimePoint_Weeks, BW_f_dat$Sex)) %>% lapply(., function(x){(aov(Weight_gain ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})
+
+BW_f_dat_test_sum2 <- lapply(seq_along(BW_f_dat_test_sum), function(x){BW_f_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_f_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
+
+ggplot(BW_f_dat, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
+    geom_point(size = 0.5, alpha = 0.5) +
+    geom_path(aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
+    stat_summary(geom = "point", fun = "mean", size = 1) +
+    stat_summary(geom = "line", fun = "mean", linetype = "dashed") +
+    geom_ribbon(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.2, color = NA) +
+    geom_point(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
+    geom_line(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
+    geom_label_repel(data = BW_f_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
     facet_grid(.~Sex) +
@@
     scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10.
-After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
-    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted starting from week 4; ANOVA test with duncan's multiple range tests were performed at each week between week 4 and 15.", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
 

### 2021-02-26 code/draft.Rmd
Finish bw gain

@@
 library(ggrepel)
-# library(ggpubr)
+library(rstatix)
 
@@
 
-## Body Weight gain relative to week 3
+## Body Weight gain relative to week 3 all data
 ```{r}
-BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])
+BW_f <- BW %>% group_by(MouseID) %>% filter(n()>1, 3 %in% TimePoint_Weeks) %>% ungroup() %>% filter(TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1], BirthMode = factor(BirthMode, levels = c("VF", "CSR", "CS")))
+BW_f %>% ungroup() %>% pivot_wider(id_cols = c(BirthMode, MouseID), names_from = TimePoint_Weeks, values_from = Weight_gain)
 
-date_range <- c(4, 16)
+date_range = seq(5, 15, by = 1)
 
-BW_f_dat <- BW_f %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])
+BW_f_2 <- BW_f %>% filter(TimePoint_Weeks %in% date_range)
+BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(names_from = c(BirthMode, Sex), values_from = N)
 
-BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(names_from = c(BirthMode, Sex), values_from = N)
-
-BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
-
-BW_f_dat_test <- BW_f_dat %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain ~ BirthMode, p.adjust.method = "none") %>% ungroup() %>% mutate(p.adj = p.adjust(p, method = "fdr"))
-
-BW_f_dat_test_tbl1 <- BW_f_dat_test %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p.adj)
-
-BW_f_dat_test_sum <- split(BW_f_dat, f = list(BW_f_dat$TimePoint_Weeks, BW_f_dat$Sex)) %>% lapply(., function(x){(aov(Weight_gain ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})
-
-BW_f_dat_test_sum2 <- lapply(seq_along(BW_f_dat_test_sum), function(x){BW_f_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_f_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
-
-ggplot(BW_f_dat, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
-    geom_point(size = 0.5, alpha = 0.5) +
-    geom_path(aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
-    stat_summary(geom = "point", fun = "mean", size = 1) +
-    stat_summary(geom = "line", fun = "mean", linetype = "dashed") +
-    geom_ribbon(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.2, color = NA) +
-    geom_point(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
-    geom_line(data = BW_f_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
-    geom_label_repel(data = BW_f_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
+ggplot(BW_f_2, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
+    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
     facet_grid(.~Sex) +
@@
     scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted starting from week 4; ANOVA test with duncan's multiple range tests were performed at each week between week 4 and 15.", width = 120)) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(g)", title = "C-Section Restoration Project - Body Weight Gain", subtitle = str_wrap("LOESS smooth with 95% CI", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.7, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_gain_smooth.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+BW_f_2_sum <- BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
+
+BW_f_2_sum %>% pivot_wider(id_cols = c(BirthMode, Sex), names_from = TimePoint_Weeks, values_from = N) %>% View()
+
+BW_f_2_stat <- (BW_f_2 %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain~BirthMode) %>% mutate(p = round(p, 3)) %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p))[c(2, 3, 1, 5, 6, 4), ] %>% unite(Compare, group1, group2, sep = "-") %>% View
+
+p = ggplot(BW_f_2_sum, aes(x = TimePoint_Weeks, y = Mean, color = BirthMode)) +
+    geom_point(data = BW_f_2, aes(y = Weight_gain), size = 0.5, alpha = 0.5) +
+    geom_path(data = BW_f_2, aes(y = Weight_gain, group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
+    geom_ribbon(aes(y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.4, color = NA) +
+    geom_point(size = 1.5) +
+    geom_line() +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(g)", title = "C-Section Restoration Project - Body Weight Gain", subtitle = str_wrap("Mean and 95% CI were plotted.", width = 120)) +
     theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+print(p)
+set_panel_size(file = "results/figs/exploratory/BW_gain_mean_ci.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
 
@@
 
+## Body Weight gain relative to week 3 pre-covid
+```{r}
+BW_f <- BW %>% group_by(MouseID) %>% filter(n()>1, 3 %in% TimePoint_Weeks, !Batch %in% c("Batch9", "Batch10")) %>% ungroup() %>% filter(TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1], BirthMode = factor(BirthMode, levels = c("VF", "CSR", "CS")))
+BW_f %>% ungroup() %>% pivot_wider(id_cols = c(BirthMode, MouseID), names_from = TimePoint_Weeks, values_from = Weight_gain)
+
+date_range = seq(5, 15, by = 1)
+
+BW_f_2 <- BW_f %>% filter(TimePoint_Weeks %in% date_range)
+BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(names_from = c(BirthMode, Sex), values_from = N)
+
+ggplot(BW_f_2, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
+    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(g)", title = "C-Section Restoration Project - Body Weight Gain", subtitle = str_wrap("LOESS smooth with 95% CI", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.7, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_gain_smooth_precovid.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+BW_f_2_sum <- BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
+
+BW_f_2_sum %>% pivot_wider(id_cols = c(BirthMode, Sex), names_from = TimePoint_Weeks, values_from = N) %>% View()
+
+BW_f_2_stat <- (BW_f_2 %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain~BirthMode) %>% mutate(p = round(p, 3)) %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p))[c(2, 3, 1, 5, 6, 4), ] %>% unite(Compare, group1, group2, sep = "-") %>% View
+
+p = ggplot(BW_f_2_sum, aes(x = TimePoint_Weeks, y = Mean, color = BirthMode)) +
+    geom_point(data = BW_f_2, aes(y = Weight_gain), size = 0.5, alpha = 0.5) +
+    geom_path(data = BW_f_2, aes(y = Weight_gain, group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
+    geom_ribbon(aes(y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.4, color = NA) +
+    geom_point(size = 1.5) +
+    geom_line() +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(g)", title = "C-Section Restoration Project - Body Weight Gain", subtitle = str_wrap("Mean and 95% CI were plotted.", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+print(p)
+set_panel_size(file = "results/figs/exploratory/BW_gain_mean_ci_precovid.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+```
 ## DEXA

### 2021-03-01 code/draft.Rmd
Finished draft

--- 2021-02-25 code/draft.Rmd
@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 # Loading library here
-library(conflicted)
 library(knitr)
 library(tidyverse)
-library(extrafont)
 library(readxl)
 library(ggrepel)
-library(ggpubr)
-
-conflict_prefer("filter", "dplyr")
-conflict_prefer("lag", "dplyr")
+library(rstatix)
 
@@
 
+BM_colors = c("#377EB8", "#4DAF4A", "#E41A1C", "purple")
+names(BM_colors) = c("VF", "CSR", "CS", "VD")
 sessionInfo()
@@
     scale_y_continuous(breaks = seq(2, y_max, 4)) +
-    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
     labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight Plots-AllData") +
-    theme_Publication() + theme(panel.grid.minor = element_blank())
+    theme_jw() + theme(panel.grid.minor = element_blank())
 ```
@@
 
-BW_sum2 %>% mutate(Count = paste0(N, "(", N_family, ")")) %>% select(BirthMode, Sex, TimePoint_Weeks, Count) %>% spread(key = TimePoint_Weeks, value = Count) %>% View
+BW_sum2 %>% mutate(Count = paste0(N, "(", N_family, ")")) %>% select(BirthMode, Sex, TimePoint_Weeks, Count) %>% spread(key = TimePoint_Weeks, value = Count)
 ```
@@
 ```{r}
-date_range <- c(2, BW_sum2$TimePoint_Weeks[BW_sum2$N_family>=5] %>% max)
+#date_range <- c(2, BW_sum2$TimePoint_Weeks[BW_sum2$N_family>=5] %>% max)
+date_range <- seq(3, 15, by = 1)
 
-BW_dat <- BW %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])
+BW_dat <- BW %>% dplyr::filter(TimePoint_Weeks %in% date_range)
 
-BW_dat_stat_sum <- BW_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_g) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
-
-BW_dat_test_sum <- split(BW_dat, f = list(BW_dat$TimePoint_Weeks, BW_dat$Sex)) %>% lapply(., function(x){(aov(Weight_g ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})
-
-BW_dat_test_sum2 <- lapply(seq_along(BW_dat_test_sum), function(x){BW_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
+BW_dat_sum <- BW_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_g) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
 
 ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
-    geom_point(data = BW, size = 0.5, alpha = 0.5) +
-    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
-    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
-    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
-    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
-    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
-    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
-    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
+    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
     facet_grid(.~Sex) +
     scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
-    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10.
-After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
-    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
-set_panel_size(file = "results/figs/exploratory/BW.pdf", width = unit(4, "in"), height = unit(3.2, "in"), useDingbats = F)
-```
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
+    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "IFNHCSR-BodyWeight", subtitle = str_wrap("LOESS smooth with 95% CI", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_smooth.pdf", width = unit(3, "in"), height = unit(2.4, "in"))
 
-## Body Weight gain relative to week 2
-```{r}
-BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20200701-JW.xlsx"), sheet = "BodyWeightRecords") %>% filter(!is.na(Weight_g))
-BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))
+BW_dat_stat <- BW_dat %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_g~BirthMode) %>% mutate(p.adj = p.adjust(p, "fdr") %>% round(., 3), p = round(p, 3))
 
-BW_f <- BW %>% filter(ExperimentSet=="Set1-BW", TimePoint_Weeks!=1) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = Weight_g - Weight_g[1])
-
-date_range <- c(2, 10)
-
-BW_f_dat <- BW_f %>% filter(TimePoint_Weeks<=date_range[2], TimePoint_Weeks>=date_range[1])
-
-BW_f_dat_stat_sum <- BW_f_dat %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n())
-
-%>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
-
-BW_dat_test_sum <- split(BW_dat, f = list(BW_dat$TimePoint_Weeks, BW_dat$Sex)) %>% lapply(., function(x){(aov(Weight_g ~ BirthMode, data = x) %>% agricolae::duncan.test(trt = "BirthMode", console = T))$groups %>% rownames_to_column(var = "BirthMode")})
-
-BW_dat_test_sum2 <- lapply(seq_along(BW_dat_test_sum), function(x){BW_dat_test_sum[[x]] %>% mutate(Weeks_sex = names(BW_dat_test_sum)[[x]]) %>% separate(Weeks_sex, into = c("TimePoint_Weeks", "Sex"), sep = "\\.")}) %>% do.call("rbind",.) %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
-
-ggplot(BW_dat, aes(x = TimePoint_Weeks, y = Weight_g, color = BirthMode)) +
-    geom_point(data = BW, size = 0.5, alpha = 0.5) +
-    geom_path(data = BW, aes(group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
-    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "point", fun = "mean", size = 1) +
-    stat_summary(data = BW %>% filter(TimePoint_Weeks>=10), geom = "line", fun = "mean", linetype = "dashed") +
-    geom_ribbon(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.3) +
-    geom_point(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean), size = 1.5) +
-    geom_line(data = BW_dat_stat_sum, aes(x = TimePoint_Weeks, y = Mean)) +
-    geom_label_repel(data = BW_dat_test_sum2, aes(label = groups), size = 6/.pt, label.padding = 0.1) +
+p = ggplot(BW_dat_sum, aes(x = TimePoint_Weeks, y = Mean, color = BirthMode)) +
+    geom_point(data = BW_dat, aes(y = Weight_g), size = 0.5, alpha = 0.5) +
+    geom_path(data = BW_dat, aes(y = Weight_g, group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
+    geom_ribbon(aes(y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.4, color = NA) +
+    geom_point(size = 1.5) +
+    geom_line() +
     facet_grid(.~Sex) +
     scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
-    scale_color_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    scale_fill_manual(values = c("#377EB8", "#4DAF4A", "#E41A1C")) +
-    labs(x = "Sampling_Week", y = "Body Weight(g)", title = "C-Section Restoration Project - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted between week 2 and 10; ANOVA test with duncan's multiple range tests were performed at each week between week 2 and 10.
-After week 10, only mean of each group was plotted due to very low sample size", width = 120)) +
-    theme_Publication() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
+    labs(x = "Sampling_Week", y = "Body Weight (g)", title = "IFNHCSR - Body Weight", subtitle = str_wrap("Mean and 95% CI were plotted.", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+print(p)
+set_panel_size(file = "results/figs/exploratory/BW_mean_ci.pdf", width = unit(3, "in"), height = unit(2.4, "in"))
+
+ggplot(BW_dat_stat, aes(x = TimePoint_Weeks, y = p.adj, color = paste(group1, group2, sep = "-"))) +
+    geom_point() +
+    geom_line() +
+    geom_hline(yintercept = 0.05, linetype = "dashed", color = "black") +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) +
+    scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3')) +
+    labs(x = "Sampling_Week", y = "FDR adjusted p-value", title = "IFNHCSR - P-value for body weight", color = "Comparison") +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_p_fdr.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
 
@@
 
+## Body Weight gain relative to week 3 all data
+```{r}
+BW_f <- BW %>% group_by(MouseID) %>% filter(n()>1, 3 %in% TimePoint_Weeks) %>% ungroup() %>% filter(TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = (Weight_g - Weight_g[1])/Weight_g[1]*100, BirthMode = factor(BirthMode, levels = c("VF", "CSR", "CS")))
+BW_f %>% ungroup() %>% pivot_wider(id_cols = c(BirthMode, MouseID), names_from = TimePoint_Weeks, values_from = Weight_gain)
+
+date_range = seq(4, 15, by = 1)
+
+BW_f_2 <- BW_f %>% filter(TimePoint_Weeks %in% date_range)
+BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(id_cols = c(BirthMode, Sex), names_from = TimePoint_Weeks, values_from = N)
+
+ggplot(BW_f_2, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
+    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(%)", title = "IFNHCSR - Body Weight Gain", subtitle = str_wrap("LOESS smooth with 95% CI", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.7, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_gain_smooth.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+BW_f_2_sum <- BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "/"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "/", convert = T) %>% ungroup
+
+BW_f_2_sum %>% pivot_wider(id_cols = c(BirthMode, Sex), names_from = TimePoint_Weeks, values_from = N)
+
+BW_f_2_stat <- BW_f_2 %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain~BirthMode) %>% ungroup() %>% mutate(p.adj = p.adjust(p, "fdr") %>% round(., 3), p = round(p, 3))
+
+BW_f_2_stat_sum <- (BW_f_2_stat %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p))[c(2, 3, 1, 5, 6, 4), ] %>% unite(Compare, group1, group2, sep = "-")
+
+p = ggplot(BW_f_2_sum, aes(x = TimePoint_Weeks, y = Mean, color = BirthMode)) +
+    geom_point(data = BW_f_2, aes(y = Weight_gain), size = 0.5, alpha = 0.5) +
+    geom_path(data = BW_f_2, aes(y = Weight_gain, group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
+    geom_ribbon(aes(y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.4, color = NA) +
+    geom_point(size = 1.5) +
+    geom_line() +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(%)", title = "IFNHCSR - Body Weight Gain", subtitle = str_wrap("Mean and 95% CI were plotted.", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+print(p)
+set_panel_size(file = "results/figs/exploratory/BW_gain_mean_ci.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+ggplot(BW_f_2_stat, aes(x = TimePoint_Weeks, y = p.adj, color = paste(group1, group2, sep = "-"))) +
+    geom_point() +
+    geom_line() +
+    geom_hline(yintercept = 0.05, linetype = "dashed", color = "black") +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) +
+    scale_color_manual(values = c('#1b9e77','#d95f02','#7570b3')) +
+    labs(x = "Sampling_Week", y = "FDR adjusted p-value", title = "IFNHCSR - P-value for body weight gain", color = "Comparison") +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_gain_p_fdr.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+```
+
+## Body Weight gain relative to week 3 pre-covid
+```{r}
+BW_f <- BW %>% group_by(MouseID) %>% filter(n()>1, 3 %in% TimePoint_Weeks, !Batch %in% c("Batch9", "Batch10")) %>% ungroup() %>% filter(TimePoint_Weeks>=3) %>% arrange(TimePoint_Weeks) %>% group_by(MouseID) %>% mutate(Weight_gain = (Weight_g - Weight_g[1])/Weight_g[1]*100, BirthMode = factor(BirthMode, levels = c("VF", "CSR", "CS")))
+BW_f %>% ungroup() %>% pivot_wider(id_cols = c(BirthMode, MouseID), names_from = TimePoint_Weeks, values_from = Weight_gain)
+
+date_range = seq(4, 15, by = 1)
+
+BW_f_2 <- BW_f %>% filter(TimePoint_Weeks %in% date_range)
+BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(N = n()) %>% pivot_wider(names_from = c(BirthMode, Sex), values_from = N)
+
+ggplot(BW_f_2, aes(x = TimePoint_Weeks, y = Weight_gain, color = BirthMode)) +
+    geom_smooth(aes(fill = BirthMode), alpha = 0.3) +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(%)", title = "IFNHCSR - Body Weight Gain", subtitle = str_wrap("LOESS smooth with 95% CI", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.7, plot.title = element_text(hjust = 0))
+set_panel_size(file = "results/figs/exploratory/BW_gain_smooth_precovid.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+BW_f_2_sum <- BW_f_2 %>% group_by(TimePoint_Weeks, BirthMode, Sex) %>% summarise(Mean_cl = Hmisc::smean.cl.normal(x = Weight_gain) %>% paste(collapse = "-"), N = n()) %>% separate(Mean_cl, into = c("Mean", "Lwr", "Uwr"), sep = "-", convert = T) %>% ungroup
+
+BW_f_2_sum %>% pivot_wider(id_cols = c(BirthMode, Sex), names_from = TimePoint_Weeks, values_from = N) %>% View()
+
+BW_f_2_stat <- BW_f_2 %>% group_by(TimePoint_Weeks, Sex) %>% t_test(Weight_gain~BirthMode) %>% ungroup() %>% mutate(p.adj = p.adjust(p, "fdr") %>% round(., 3), p = round(p, 3))
+
+BW_f_2_stat_sum <- (BW_f_2_stat %>% pivot_wider(id_cols = c(Sex, group1, group2), names_from = TimePoint_Weeks, values_from = p))[c(2, 3, 1, 5, 6, 4), ] %>% unite(Compare, group1, group2, sep = "-")
+
+p = ggplot(BW_f_2_sum, aes(x = TimePoint_Weeks, y = Mean, color = BirthMode)) +
+    geom_point(data = BW_f_2, aes(y = Weight_gain), size = 0.5, alpha = 0.5) +
+    geom_path(data = BW_f_2, aes(y = Weight_gain, group = MouseNo), color = "grey", size = 0.5, alpha = 0.5) +
+    geom_ribbon(aes(y = Mean, ymin = Lwr, ymax = Uwr, fill = BirthMode), alpha = 0.4, color = NA) +
+    geom_point(size = 1.5) +
+    geom_line() +
+    facet_grid(.~Sex) +
+    scale_x_continuous(breaks = c(seq(2, 18, 1))) + 
+    scale_color_manual(values = BM_colors) +
+    scale_fill_manual(values = BM_colors) +
+    labs(x = "Sampling_Week", y = "Body Weight Gain(%)", title = "IFNHCSR - Body Weight Gain", subtitle = str_wrap("Mean and 95% CI were plotted.", width = 120)) +
+    theme_jw() + theme(panel.grid.minor = element_blank(), aspect.ratio = 0.8, plot.title = element_text(hjust = 0))
+print(p)
+set_panel_size(file = "results/figs/exploratory/BW_gain_mean_ci_precovid.pdf", width = unit(3, "in"), height = unit(2.1, "in"))
+
+```
 ## DEXA

### 2021-05-13 code/draft.Rmd
responder test

@@
 
-source("~/Dropbox/42-JCHWANG-RUTGERS/Projects-Rutgers/Src/utils.R")
+source("code/utils.R")
 
@@
 ```{r}
-BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20210224-HS.xlsx"), sheet = "BodyWeightRecords", range = "A1:T2009") %>% filter(!is.na(Weight_g))
+BW <- read_excel(paste0(path_rec, "MasterMetadata-CS-SW-Oct2019-20210402-HS.xlsx"), sheet = "BodyWeightRecords", range = "A1:T2009") %>% filter(!is.na(Weight_g))
 BW$BirthMode = factor(BW$BirthMode, levels = c("VF", "CSR", "CS"))
@@
 
+```{r}
+n_sd = 1.5
+
+BW_f_vf_range = BW_f %>% ungroup %>% filter(BirthMode=="VF") %>% group_by(Sex, TimePoint_Weeks) %>% summarise(summ = Hmisc::smean.sdl(Weight_g, mult = n_sd) %>% paste(collapse = ";")) %>% separate(summ, into = c("vf_mean", "vf_ll", "vf_ul"), sep = ";")
+
+BW_f_3 = merge(BW_f, BW_f_vf_range, by = c("Sex", "TimePoint_Weeks")) %>% filter(TimePoint_Weeks<=15) %>% mutate(Flag = ifelse(Weight_g > vf_ul, "Overweight", ifelse(Weight_g < vf_ll, "Underweight", "Normal")))
+
+ggplot(BW_f_3, aes(x = TimePoint_Weeks, y = Weight_g)) +
+    geom_point(size = 1.5, aes(color = Flag)) +
+    geom_line(aes(group = MouseID, color = Flag)) +
+    stat_summary(data = BW_f_3 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#377EB8", alpha = 0.3) +
+    stat_summary(data = BW_f_3 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "line", fun = "mean", color = "#377EB8", size = 1) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#E41A1C", alpha = 0.3) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "line", fun.y = "mean", color = "#E41A1C", size = 1) +
+    facet_grid(Sex ~ BirthMode) +
+    scale_color_manual(values = c("Overweight" = "red", "Normal" = "grey30", "Underweight" = "green")) +
+    theme_jw(base_size = 18) + theme(aspect.ratio = 0.8) +
+    scale_x_continuous(breaks = seq(4, 15, 2)) +
+    labs(x = "Weeks", y = "Body Weight (g)")
+
+BW_f_3 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% mutate(OR_over = N_over/(N_sub-N_over)/(N_over[1]/(N_sub[1]-N_over[1])))
+```
+
+```{r}
+n_sd = 1.5
+
+BW_f_vf_range = BW_f %>% ungroup %>% filter(BirthMode=="VF") %>% group_by(Sex, TimePoint_Weeks) %>% summarise(summ = Hmisc::smean.sdl(Weight_gain, mult = n_sd) %>% paste(collapse = ";")) %>% separate(summ, into = c("vf_mean", "vf_ll", "vf_ul"), sep = ";", convert = T)
+
+BW_f_4 = merge(BW_f, BW_f_vf_range, by = c("Sex", "TimePoint_Weeks")) %>% ungroup %>% filter(TimePoint_Weeks<=15) %>% mutate(Flag = ifelse(Weight_gain > vf_ul, "Overweight", ifelse(Weight_gain < vf_ll, "Underweight", "Normal")))
+
+ggplot(BW_f_4, aes(x = TimePoint_Weeks, y = Weight_gain)) +
+    geom_point(size = 1.5, aes(color = Flag)) +
+    geom_line(aes(group = MouseID, color = Flag)) +
+    stat_summary(data = BW_f_4 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#377EB8", alpha = 0.3) +
+    stat_summary(data = BW_f_4 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "line", fun = "mean", color = "#377EB8", size = 1) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#E41A1C", alpha = 0.3) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "line", fun.y = "mean", color = "#E41A1C", size = 1) +
+    facet_grid(Sex ~ BirthMode) +
+    scale_color_manual(values = c("Overweight" = "red", "Normal" = "grey30", "Underweight" = "green")) +
+    theme_jw(base_size = 18) + theme(aspect.ratio = 0.8) +
+    scale_x_continuous(breaks = seq(4, 15, 2)) +
+    labs(x = "Weeks", y = "Body Weight gain(% to week 3 body weight)")
+
+BW_f_4 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% mutate(OR_over = N_over/(N_sub-N_over)/(N_over[1]/(N_sub[1]-N_over[1])))
+```
+
 ## Body Weight gain relative to week 3 pre-covid

### 2021-05-13 code/utils.R

@@ -1,0 +1,185 @@
+theme_jw <- function(base_size=10) {
+    require(grid)
+    require(ggthemes)
+    (theme_foundation(base_size=base_size)
+        + theme(text = element_text(),
+                panel.background = element_rect(colour = NA),
+                plot.background = element_rect(colour = NA),
+                panel.border = element_rect(colour = NA),
+                axis.title = element_text(face = "bold", size = rel(1), color = "black"),
+                axis.title.y = element_text(angle=90, vjust =2),
+                axis.title.x = element_text(vjust = -0.2),
+                axis.text = element_text(size = rel(0.8), color = "black"),
+                axis.line = element_line(color = "black", size = 0.2),
+                axis.ticks = element_line(color = "black", size = 0.2),
+                panel.grid.major = element_line(color = "grey", size = 0.1),
+                panel.grid.minor = element_line(color = "grey", size = 0.1),
+                legend.key = element_rect(colour = NA),
+                legend.position = "right",
+                legend.direction = "vertical",
+                legend.key.size= unit(0.4, "cm"),
+                legend.title = element_text(face="bold.italic", size = rel(1.0)),
+                legend.text=element_text(size = rel(1.0)),
+                plot.margin=unit(c(1,0.5,0.5,0.5),"lines"),
+                plot.title = element_text(hjust = 0, vjust = 1, size = rel(1.2), face = "bold"), 
+                plot.title.position = "panel",
+                strip.background=element_rect(colour="black",fill="black"),
+                strip.text = element_text(face="bold", color = "white", size = rel(1))
+        ))
+}
+
+merge_iter <- function(x, by){
+    # This function is used to iteratively merge dataframe of the same structure from a list
+    #
+    # Arguments:
+    #   x, the list storing the dataframes
+    #   by, either a single value indicating the column that will be used as key column by all dataframes; or a vector of the same length of x, which stores the number of key column.
+    #
+    # Return:
+    #   A merged dataframe.
+    ll <- length(x)
+    if (length(by) > 1 & length(by) != ll){
+        return("Error in by")
[…]

### 2021-05-14 code/draft.Rmd
responder test2

--- 2021-03-01 code/draft.Rmd
@@
 ```
+## Responders vs Non-responders
+```{r}
+n_sd = 1
+
+BW_f_vf_range = BW_f %>% ungroup %>% filter(BirthMode=="VF") %>% group_by(Sex, TimePoint_Weeks) %>% summarise(summ = Hmisc::smean.sdl(Weight_g, mult = n_sd) %>% paste(collapse = ";")) %>% separate(summ, into = c("vf_mean", "vf_ll", "vf_ul"), sep = ";")
+
+BW_f_3 = merge(BW_f, BW_f_vf_range, by = c("Sex", "TimePoint_Weeks")) %>% filter(TimePoint_Weeks<=15) %>% mutate(Flag = ifelse(Weight_g > vf_ul, "Overweight", ifelse(Weight_g < vf_ll, "Underweight", "Normal")))
+
+ggplot(BW_f_3 %>% mutate(BirthMode = factor(BirthMode, levels = c("CS", "CSR", "VF"))), aes(x = TimePoint_Weeks, y = Weight_g)) +
+    geom_point(size = 1, aes(color = Flag)) +
+    geom_line(aes(group = MouseID, color = Flag), size = 0.3) +
+    stat_summary(data = BW_f_3 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#377EB8", alpha = 0.2) +
+    stat_summary(data = BW_f_3 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "line", fun = "mean", color = "#377EB8", size = 2) +
+    annotate("segment", x=-Inf, xend = Inf, y = -Inf, yend = -Inf) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#E41A1C", alpha = 0.3) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "line", fun.y = "mean", color = "#E41A1C", size = 1) +
+    facet_grid(Sex ~ BirthMode) +
+    scale_color_manual(values = c("Overweight" = "red", "Normal" = "grey30", "Underweight" = "green")) +
+    theme_jw(base_size = 18) + theme(aspect.ratio = 0.8) +
+    scale_x_continuous(breaks = seq(4, 15, 2)) +
+    labs(x = "Weeks", y = "Body Weight (g)")
+
+BW_f_3_or_dat <- BW_f_3 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% ungroup()
+
+BW_f_3_or <- BW_f_3_or_dat %>% split(., .$Sex) %>% lapply(., function(y){y %>% mutate(N_normal = N_sub - N_over - N_under) %>% select(BirthMode, N_normal, N_over) %>% column_to_rownames(var = "BirthMode") %>% as.matrix() %>% oddsratio.fisher()})
+
+lapply(BW_f_3_or, function(x){merge(merge(as.data.frame(x$data)[1:3, 1:2], as.data.frame(x$measure), by = 0), as.data.frame(x$p.value)[2], by.x = 1, by.y = 0)}) %>% data.table::rbindlist(idcol = "Sex")
+
+```
+
+```{r}
+n_sd = 1
+
+BW_f_vf_range = BW_f %>% ungroup %>% filter(BirthMode=="VF") %>% group_by(Sex, TimePoint_Weeks) %>% summarise(summ = Hmisc::smean.sdl(Weight_gain, mult = n_sd) %>% paste(collapse = ";")) %>% separate(summ, into = c("vf_mean", "vf_ll", "vf_ul"), sep = ";", convert = T)
+
+BW_f_4 = merge(BW_f, BW_f_vf_range, by = c("Sex", "TimePoint_Weeks")) %>% ungroup %>% filter(TimePoint_Weeks<=15) %>% mutate(Flag = ifelse(Weight_gain > vf_ul, "Overweight", ifelse(Weight_gain < vf_ll, "Underweight", "Normal")))
+
+ggplot(BW_f_4 %>% mutate(BirthMode = factor(BirthMode, levels = c("CS", "CSR", "VF"))), aes(x = TimePoint_Weeks, y = Weight_gain)) +
+    geom_point(size = 1, aes(color = Flag)) +
+    geom_line(aes(group = MouseID, color = Flag), size = 0.3) +
+    stat_summary(data = BW_f_4 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#377EB8", alpha = 0.2) +
+    stat_summary(data = BW_f_4 %>% filter(BirthMode=="VF") %>% select(-BirthMode), geom = "line", fun = "mean", color = "#377EB8", size = 2) +
+    annotate("segment", x=-Inf, xend = Inf, y = -Inf, yend = -Inf) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "ribbon", fun.data = "mean_sdl", fun.args = list(mult = n_sd), fill = "#E41A1C", alpha = 0.3) +
+    #stat_summary(data = BW_f %>% filter(BirthMode=="CS") %>% select(-BirthMode), geom = "line", fun.y = "mean", color = "#E41A1C", size = 1) +
+    facet_grid(Sex ~ BirthMode) +
+    scale_color_manual(values = c("Overweight" = "red", "Normal" = "grey30", "Underweight" = "green")) +
+    theme_jw(base_size = 18) + theme(aspect.ratio = 0.8) +
+    scale_x_continuous(breaks = seq(4, 15, 2)) +
+    labs(x = "Weeks", y = "Body Weight gain(% to week 3 body weight)")
+
+BW_f_4_or_dat <- BW_f_4 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% ungroup()
+
+BW_f_4_or <- BW_f_4_or_dat %>% split(., .$Sex) %>% lapply(., function(y){y %>% mutate(N_normal = N_sub - N_over - N_under) %>% select(BirthMode, N_normal, N_over) %>% column_to_rownames(var = "BirthMode") %>% as.matrix() %>% oddsratio.fisher()})
+
+lapply(BW_f_4_or, function(x){merge(merge(as.data.frame(x$data)[1:3, 1:2], as.data.frame(x$measure), by = 0), as.data.frame(x$p.value)[2], by.x = 1, by.y = 0)}) %>% data.table::rbindlist(idcol = "Sex")
+```
 

### 2021-05-16 code/draft.Rmd
Add prevalence graph

@@
 library(rstatix)
+library(ggpubr)
+library(epitools)
 
@@
 
+BW_f_3_w15 <- BW_f_3 %>% filter(TimePoint_Weeks==15) %>% group_by(Sex) %>% pairwise_t_test(Weight_g ~ BirthMode, p.adjust.method = "fdr") %>% add_y_position(step.increase = 0.05) %>% p_format(p.adj, leading.zero = FALSE, accuracy = 0.001)
+
+ggplot(BW_f_3 %>% filter(TimePoint_Weeks==15), aes(x = BirthMode, y = Weight_g)) +
+    geom_boxplot(outlier.shape = NA, width = 0.5) +
+    geom_beeswarm(aes(color = BirthMode), cex = 2.5, show.legend = F) +
+    stat_pvalue_manual(BW_f_3_w15, label = "p.adj", tip.length = 0.01, hide.ns = T) +
+    facet_grid(.~Sex) +
+    theme_jw(base_size = 14) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+    scale_color_manual(values = BM_colors) +
+    labs(x = "Birth Mode", y = "Body Weight (g)", subtitle = "Pairwise t-test with FDR adjustments did not reveal any statistical significance")
+
+BW_f_3_ow <- BW_f_3 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(Pct_over = sum(Flag=="Overweight")/n())
+BW_f_3_ow_stats_dat <- BW_f_3 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(N_sub = n(), N_over = sum(Flag=="Overweight"), N_under = sum(Flag=="Underweight"))
+BW_f_3_ow_stats <- BW_f_3_ow_stats_dat %>% arrange(Sex, TimePoint_Weeks, BirthMode) %>% ungroup %>% split(., list(.$Sex, .$TimePoint_Weeks)) %>% lapply(., function(y){y %>% mutate(N_normal = N_sub - N_over - N_under) %>% select(BirthMode, N_normal, N_over) %>% column_to_rownames(var = "BirthMode") %>% as.matrix() %>% oddsratio.fisher()}) %>% lapply(., function(x){merge(merge(as.data.frame(x$data)[1:4, 1:2], as.data.frame(x$measure), by = 0), as.data.frame(x$p.value)[2], by.x = 1, by.y = 0)}) %>% data.table::rbindlist(idcol = "Sex.Weeks") %>% separate(Sex.Weeks, into = c("Sex", "TimePoint_Weeks"), sep = "\\.") %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
+
+BW_f_3_ow_ = full_join(BW_f_3_ow, BW_f_3_ow_stats, by = c("Sex" = "Sex", "TimePoint_Weeks"="TimePoint_Weeks", "BirthMode"="Row.names")) %>% mutate(q.fdr = p.adjust(fisher.exact, method = "fdr"), sig = case_when(q.fdr<=0.001 ~ "***", q.fdr<=0.01 ~ "**", q.fdr <=0.05 ~ "*", T ~ NA_character_))
+
+ggplot(BW_f_3_ow_, aes(x = TimePoint_Weeks, y = Pct_over, color = BirthMode)) +
+    geom_point(size = 2) +
+    geom_line(size = 1) +
+    geom_text(aes(label = sig), na.rm = T,  nudge_y = 0.05, show.legend = F) + 
+    annotate("segment", x=-Inf, xend = Inf, y = -Inf, yend = -Inf) +
+    facet_wrap(.~Sex, ncol = 1) +
+    scale_color_manual(values = BM_colors) +
+    scale_x_continuous(breaks = seq(4,15,2)) +
+    scale_y_continuous(breaks = seq(0,0.8, 0.2)) +
+    theme_jw(base_size = 14) + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank()) +
+    labs(x = "Weeks", y = "Prevalence of overweight")
+
 BW_f_3_or_dat <- BW_f_3 %>% group_by(Sex, BirthMode, MouseID) %>% filter(TimePoint_Weeks>=6) %>% summarise(N = n(), Pct_over = sum(Flag=="Overweight")/N, Pct_under = sum(Flag=="Underweight")/N) %>% mutate(Over = Pct_over>=0.7, Under = Pct_under>=0.7) %>% group_by(Sex, BirthMode) %>% summarise(N_sub = n(), N_over = sum(Over), N_under = sum(Under)) %>% ungroup()
@@
     labs(x = "Weeks", y = "Body Weight gain(% to week 3 body weight)")
+
+BW_f_4_w15 <- BW_f_4 %>% filter(TimePoint_Weeks==15) %>% group_by(Sex) %>% pairwise_t_test(Weight_g ~ BirthMode, p.adjust.method = "fdr") %>% add_y_position(step.increase = 0.05) %>% p_format(p.adj, leading.zero = FALSE, accuracy = 0.001)
+
+ggplot(BW_f_4 %>% filter(TimePoint_Weeks==15), aes(x = BirthMode, y = Weight_gain)) +
+    geom_boxplot(outlier.shape = NA, width = 0.5) +
+    geom_beeswarm(aes(color = BirthMode), cex = 2.5, show.legend = F) +
+    stat_pvalue_manual(BW_f_3_w15, label = "p.adj", tip.length = 0.01, hide.ns = T) +
+    facet_grid(.~Sex) +
+    theme_jw(base_size = 14) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+    scale_color_manual(values = BM_colors) +
+    labs(x = "Birth Mode", y = "Body Weight gain(% to week 3 body weight)", subtitle = "Pairwise t-test with FDR adjustments did not reveal any statistical significance")
+
+BW_f_4_ow <- BW_f_4 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(Pct_over = sum(Flag=="Overweight")/n())
+BW_f_4_ow_stats_dat <- BW_f_4 %>% group_by(Sex, BirthMode, TimePoint_Weeks) %>% summarise(N_sub = n(), N_over = sum(Flag=="Overweight"), N_under = sum(Flag=="Underweight"))
+BW_f_4_ow_stats <- BW_f_4_ow_stats_dat %>% arrange(Sex, TimePoint_Weeks, BirthMode) %>% ungroup %>% split(., list(.$Sex, .$TimePoint_Weeks)) %>% lapply(., function(y){y %>% mutate(N_normal = N_sub - N_over - N_under) %>% select(BirthMode, N_normal, N_over) %>% column_to_rownames(var = "BirthMode") %>% as.matrix() %>% oddsratio.fisher()}) %>% lapply(., function(x){merge(merge(as.data.frame(x$data)[1:4, 1:2], as.data.frame(x$measure), by = 0), as.data.frame(x$p.value)[2], by.x = 1, by.y = 0)}) %>% data.table::rbindlist(idcol = "Sex.Weeks") %>% separate(Sex.Weeks, into = c("Sex", "TimePoint_Weeks"), sep = "\\.") %>% mutate(TimePoint_Weeks = as.numeric(TimePoint_Weeks))
+
+BW_f_4_ow_ = full_join(BW_f_4_ow, BW_f_4_ow_stats, by = c("Sex" = "Sex", "TimePoint_Weeks"="TimePoint_Weeks", "BirthMode"="Row.names")) %>% mutate(q.fdr = p.adjust(fisher.exact, method = "fdr"), sig = case_when(q.fdr<=0.001 ~ "***", q.fdr<=0.01 ~ "**", q.fdr <=0.05 ~ "*", T ~ NA_character_))
+
+ggplot(BW_f_4_ow_, aes(x = TimePoint_Weeks, y = Pct_over, color = BirthMode)) +
+    geom_point(size = 2) +
+    geom_line(size = 1) +
+    geom_text(aes(label = sig), na.rm = T,  nudge_y = 0.05, show.legend = F) + 
+    annotate("segment", x=-Inf, xend = Inf, y = -Inf, yend = -Inf) +
+    facet_wrap(.~Sex, ncol = 1) +
+    scale_color_manual(values = BM_colors) +
+    scale_x_continuous(breaks = seq(4,15,2)) +
+    scale_y_continuous(breaks = seq(0,0.8, 0.2)) +
+    theme_jw(base_size = 14) + theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank()) +
+    labs(x = "Weeks", y = "Prevalence of overweight")
 
